### 2016-12-29 README.Rmd
update install instructions
thank Ivan Hanigan for his introduction to csv-fingerprint

library(devtools)

install_github("tierneyn/visdat")
```

@@

## Experimental features

@@

Thank you to Jenny Bryan, whose [tweet](https://twitter.com/JennyBryan/status/679011378414268416) got me thinking about vis_dat, and for her code contributions that remove a lot of testing errors.

>>>>

devtools::install_github("njtierney/visdat")
```

@@

# Experimental features

@@

Thank you to Ivan Hanigan who [first commented](http://www.njtierney.com/r/missing%20data/rbloggers/2015/12/01/ggplot-missing-data/#comment-2388263747) this suggestion after I made a blog post about an initial prototype `ggplot_missing`, and Jenny Bryan, whose [tweet](https://twitter.com/JennyBryan/status/679011378414268416) got me thinking about vis_dat, and for her code contributions that removed a lot of errors.
